### 2016-04-27 ch06-concl/conclusions.tex
Conclusions finished? + some minor stuff

>>>>

  In addition, an approach has been developed that allows to reduce the variance of the estimated \gls{FRF} when it is captured in a long data record.
  This method works by examining the estimated impulse response, i.e. the inverse \gls{DFT} of the \gls{FRF}, and estimating a truncation time $\truncTime$ beyond which the impulse response is overwhelmed by the noise.
  By truncating past this point and transforming the result back into the frequency domain, an \gls{FRF} is obtained that has a reduced \gls{RMS} error by reducing the variance due to the noise.
  Two complementary approaches to determine $\truncTime$ have been developed.
  Both methods estimate the noise level on the impulse response by assuming the last $10\%$ of the samples are only noise.
  The first method exploits the fact that many physical systems exhibit an exponential decay.
  This exponential decay is estimated roughly, such that the truncation point is determined as the instant where decay is below the noise level.
  The second method divides the impulse response into segments.
  Starting from the last segment, it is tested statistically whether the preceding segment is significantly different from the noise, such that $\truncTime$ is estimated.
